### 2014-02-14 paper/main.tex
minor updates

In practice, we currently fix the number of components $K$ to be large, and take the variances $\sigma_1<\sigma_2<\dots<\sigma_K$ to be fixed, and vary from very small to very large --  sufficiently large that typically $\hat\pi_K \approx 0$.

@@

Using a mixture of normal distributions for $g$ 
has the advantage that,
when combined with the normal likelihood, they give
an analytic form for the conditional distribution $p(\beta_j | \hat\pi, \hat\beta_j, s_j)$ (also a mixture of normals).

@@

The local False Discovery Rate (lfdr) for observation $j$ is
\begin{equation}
\lfdr_j = p(\beta_j = 0 | \hat\beta, s).
\end{equation}
The lfdr terminology comes from using "discovery" to refer to rejecting the null ($H_j:\beta_j=0$).
Specifically $\lfdr_j$ is the probability that, if we reject $H_j$,
it is a  "false discovery".

As pointed out by \cite{gelman.etal}, there are settings where
$\beta_j=0$ is implausible, in which case the lfdr is not useful: if every $\beta_j$ is non-zero then there
is no such thing as a false discovery and the lfdr will always be identically 0. 
Gelman et al suggest that in such settings we
might replace the concept of a false discovery with the
concept of an ``error in sign". The idea is that, in settings where $\beta_j=0$ is implausible, the most fundamental
inference objective is to ask which $\beta_j$ are positive and which are negative. Indeed, even in settings where some
$\beta_j$ are exactly zero, it could be argued that identifying which are positive and which negative is
fundamentally more interesting and useful than identifying which are non-zero. For example, when identifying differentially expressed genes,
analysts will often separate the genes that are ``upregulated" in one condition from those that ``downregulated" in that condition.

Motivated by this, we define the local False Sign Rate (lfsr) for observation $j$ as 
\begin{equation}
\lfsr_j := \min[ p(\beta_j \geq 0| \hat\beta, s), p(\beta_j \leq 0| \hat\beta, s) ].
\end{equation}
Thus $\lfsr_j$ gives the probability that we would get the sign of $\beta_j$ wrong if we
were to make our best guess. (Note that we count it as an error to state that $\beta$ is positive or negative when it is truly zero.)
To illustrate, suppose for concreteness
that the minimum is achieved by the first term, $p(\beta_j \geq 0| \hat\beta, s)=0.05$ say. Then
our best guess would be that $\beta$ is negative, and the probability that we have
made an error in sign would be 0.05. We note that the idea of focussing on tail areas, rather than point null hypotheses,
has a long history (e.g. Altham? others?).

@@

>>>>

@@

@@

The local False Discovery Rate (lfdr) for observation $j$ is defined \cite{efron} as
\begin{equation}
\lfdr_j = p(\beta_j = 0 | \hat\pi, \hat\beta, s).
\end{equation}
The lfdr terminology comes from using "discovery" to refer to rejecting the null ($H_j:\beta_j=0$).
Specifically $\lfdr_j$ is the probability that, if we reject $H_j$,
it is a  "false discovery".

As pointed out by \cite{gelman.etal}, there are settings where
$\beta_j=0$ is implausible, in which case the lfdr is not useful: if every $\beta_j$ is non-zero then there
is no such thing as a false discovery and the lfdr will always be identically 0. 
Gelman et al suggest that in such settings we
might replace the concept of a false discovery with the
concept of an ``error in sign". The idea is that, in settings where $\beta_j=0$ is implausible, the most fundamental
inference objective is to ask which $\beta_j$ are positive and which are negative. Indeed, even in settings where some
$\beta_j$ are exactly zero, separately identifying which are positive and which negative may be useful. For example, when identifying differentially expressed genes,
analysts will often separate the genes that are ``upregulated" in one condition from those that ``downregulated" in that condition.

Motivated by this, we define the local False Sign Rate (lfsr) for observation $j$ as 
\begin{equation}
\lfsr_j := \min[ p(\beta_j \geq 0| \hat\beta, s), p(\beta_j \leq 0| \hat\pi, \hat\beta, s) ].
\end{equation}
Thus $\lfsr_j$ gives the probability that we would get the sign of $\beta_j$ wrong if we
were to make our best guess. (Note that we count it as an error to state that $\beta$ is positive or negative when it is truly zero.)
To illustrate, suppose for concreteness
that the minimum is achieved by the first term, $p(\beta_j \geq 0| \hat\beta, s)=0.05$ say. Then
our best guess would be that $\beta$ is negative, and the probability that we have
made an error in sign would be 0.05. We note that the idea of focussing on tail areas, rather than point null hypotheses,
has a long history (e.g. Altham? others?).

@@

\subsection{Discussion}
